# [Obandit](http://freux.fr/oss/obandit.html)-`r Sys.getenv('obanditversion')` experimental validation.

The source for this experimental validation can be found [here](source.tgz)

```{r, echo=TRUE}
theme_set(theme_minimal())
scale_colour_continuous <- function(...)
       scale_colour_brewer(palette="Pastel1", ...)
scale_fill_continuous <- function(...)
       scale_fill_brewer(palette="Pastel1",...)
k=(ncol(data)-4)
setnames(data, "arm", "played")
data$played=data$played+1
data$best=as.numeric(apply(data,1,max))
data$played_loss=as.numeric(apply(data,1,function (x) unlist(x[as.integer(x["played"])])))
data$best_hindsight=data[,as.numeric(which.max(lapply(data[,1:k],mean)))]
```

```{r,echo=TRUE}
reduce_t <- function (d) {
  data.frame(
            inst_avgregret=mean(-d$played_loss+d$best_hindsight),
            t=d$t[1]
            )
}
reduce_experiment <- function (d) {
  data.frame(
            regret_t=cumsum(-d$played_loss+d$best_hindsight),
            t=d$t
            )
}
reduce_t2 <- function (d) {
  data.frame(
            avgregret=mean(d$regret_t),
            t=d$t[1]
            )
}
data_reduced=ddply(data,c("t","policy"),reduce_t)
data_reduced$avgregret=cumsum(data_reduced$inst_avgregret)
data_reduced=ddply(data,c("experiment","policy"),reduce_experiment)
data_reduced=ddply(data_reduced,c("t","policy"),reduce_t2)

```

# Gaussian thresholded arms for `r k` arms and `r nrow(data_reduced)` rounds, experimental sample size `r max(data$experiment)`.

Basic arm rewards:

```{r,echo=TRUE , fig.cap="",dev="png",fig.width=10,fig.height=4}
data_mutated = data %>% gather("arm","loss",1:k)
ggplot(data_mutated,aes(arm,loss,group=factor(arm)))+
geom_boxplot() +
labs(title ="Arm comparison", x = "Arm", y = "Average Reward", fill="Arm") +
scale_x_discrete()
```

Full summary of the data:
```{r,echo=TRUE}
print(summary(data))
```

### Performance of various algorithms.
In terms of regret to best arm in hindsight, using exp3, ucb1 and fixed-exploration epsilon-greedy:

```{r,echo=TRUE , fig.cap="",dev="png",fig.width=14,fig.height=4}
  ggplot(data_reduced,aes(t,avgregret,color=policy))+
  geom_line() +
  labs(title ="Arm comparison", x = "t", y = "Average Regret", fill="Arm") +
  scale_x_continuous()
```
